\begin{abstract}
    \addchaptertocentry{\abstractname}
    This thesis describes API Scout, an information retrieval system built for OpenAPI Specifications (OAS).
    The goal of this project is to offer researchers and developers alike a tool with which they can explore and study subsets of the plethora of OAS contained in our databases.
    This exploration could be done by researchers to, for example, study the evolution of APIs over time, or to study the structure of a specific set of APIs.
    Developers, on the other hand, can use this tool to gain some inspiration on how to structure their own OpenAPI Specification documents. \\ \\
    By employing state-of-the-art embedding techniques such as the Universal Sentence Encoder (USE) and Hierarchical Navigable Small World (HNSW) graphs, the system is able to accurately and quickly retrieve relevant OAS documents.
    Furthermore, this thesis outlines the design of the API Scout Domain Specific Language (DSL).
    This DSL aims at increasing query search precision and facilitating the creation of curated datasets thanks to a simple yet powerful syntax for representing filters on a rich set of OAS metadata and metrics. \\ \\
    The evaluation framework developed in this project is used to thoroughly test the system's accuracy and retrieval time performance.
    The findings of this evaluation show that API Scout considerably enhances the retrieval of OAS documents, setting the groundwork for future improvements, such as integrating an on-the-fly metrics computation algorithm, and a user interface to better visualize the evolution of APIs over time.
\end{abstract}
